

\documentclass{jake-resume}


\begin{document}


%     LAST UPDATED DATE

%\lastupdated


%     TITLE NAME



\namesection{Jacob}{Koll}{
\href{mailto:jacob.m.koll@gmail.com}{jacob.m.koll@gmail.com} | 563.357.9129
\vspace{10pt}
}


%     COLUMN ONE


\begin{minipage}[t]{0.30\textwidth} 


%     EDUCATION


\section{Education} 

\subsection{Georgia Tech}
\descript{MS in Computer Science}
\location{May 2020 - Present | Online}
\sectionsep

\subsection{Iowa State University}
\descript{BS in Computer Science}
\location{May 2018 | Ames, IA}
\location{ Cum. GPA: 3.10 / 4.00}
\sectionsep


%     SKILLS


\section{Skills}

\subsection{Programming | Scripting}
\location{Confident:}
\textbullet{C++} \textbullet{Python} \\ 
\vspace{\topsep}
\location{Intermediate:}
\textbullet{Java} \textbullet{C} \textbullet{Make} \textbullet{CMake} \\ \textbullet{Bash} \textbullet{Corba} \textbullet{Json} \textbullet{\LaTeX} \\
\vspace{\topsep}
\location{Familiar:}
\textbullet{C\#} \textbullet{JavaScript} \textbullet{CSS} \\
\textbullet{html} \textbullet{SQL} \\
\sectionsep


\section{Interests}

\textbullet{Applications of automation using artificial intelligence as a conduit.} \\
\vspace{10pt}
\textbullet{Applications of artificial intelligence in computer security.} \\
\vspace{10pt}
\textbullet{Artificial intelligence using the human brain as a model.} \\
\vspace{10pt}
\textbullet{Evolutionary, auto-generation, and parallel processing algorithms.} \\
\sectionsep


%     COLUMN TWO


\end{minipage}%
\hfill
\begin{minipage}[t]{0.66\textwidth} 


%     EXPERIENCE


\section{Experience}
\runsubsection{Collins Aerospace}
\descript{| Software Engineer}
\location{June 2018 – Present | Cedar Rapids, IA}
\vspace{\topsep}
\vspace{\topsep}
\begin{tightemize}
\item Design, implement, and test high-level software by using object oriented design and parallel programming techniques with C++ and Python. \vspace{10pt}
\item Develop infrastructures to support model-based automated code generation, automated building, continuous integration and testing. \vspace{10pt}
\item Design scripts, tools, and applications for Windows and Linux environments with Bash, Python, and C++. \vspace{10pt}
\item Participate in all phases of the software development life cycle using Agile development practices following the Scaled Agile Framework.
\end{tightemize}
\sectionsep

\runsubsection{Iowa State University}
\descript{| Object Oriented Programming T.A.}
\location{Jan 2017 – May 2017, \ Aug 2017 – Dec 2017 | Ames, IA}
\vspace{\topsep}
\begin{tightemize}
\item Taught fundamental basics of object oriented design and best programming practices with Java through weekly labs and office hours. \vspace{10pt}
\item Addressed questions students had regarding course content and graded coursework via automated testing and code inspection. \vspace{10pt} 
\end{tightemize}
\sectionsep

\runsubsection{Iowa State University}
\descript{| Data Structures T.A.}
\location{Aug 2016 – Dec 2016, \ Aug 2017 – Dec 2017 | Ames, IA}
\vspace{\topsep}
\begin{tightemize}
\item Taught data structures and best programming practices in terms of object oriented design with Java through weekly recitations and office hours. \vspace{10pt}
\item Addressed questions students had regarding course content and graded coursework via automated testing and code inspection. \vspace{10pt}
\end{tightemize}
\sectionsep

\runsubsection{Next Era Energy}
\descript{| Software Engineering Intern }
\location{June 2016 – Aug 2016 | Juno Beach, FL}
\vspace{\topsep}
\begin{tightemize}
\item Designed, implemented, and tested web applications by using the ASP.net framework, primarily with C\#. \vspace{10pt}
\item Built a web application using C\#, JQuery, and SQL to upload, download, and view documents. \vspace{10pt}
\end{tightemize}
\end{minipage}%
\end{document}
